[dcpo_demsupport]

### 2020-08-05 paper/dcpo_demsupport.Rmd
finish labeling lag(sigma, 1) in dotwhisker plot

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(sigma, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

>>>>

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
